\documentclass[phd,tocprelim]{cornell}
%
% tocprelim option must be included to put the roman numeral pages in the
% table of contents
%
% The cornellheadings option will make headings completely consistent with
% guidelines.
%
% This sample document was originally provided by Blake Jacquot, and
% fixed up by Andrew Myers.
%
%Some possible packages to include

%\usepackage{graphicx,pstricks}
%\usepackage{graphics}
%\usepackage{moreverb}
%\usepackage{subfigure}
%\usepackage{subfigure}

%\usepackage{subfig}
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{hangcaption}
\usepackage{txfonts}
\usepackage{palatino}
\usepackage{longtable}
\usepackage{chapterbib}
\usepackage[round]{natbib}
\usepackage{epstopdf}
\usepackage{hyperref}
\hypersetup{
    pdftitle={A Graph Theoretic Approach to Food Combination Problems},
    pdfauthor={Michael Arden Nestrud},
    pdfsubject={Sensory Evaluation},
    pdfkeywords={sensory,graph theory,combinations,menus},
    linktoc=all, %link table of contents to body
    pagebackref=TRUE, %link references back to pages
    pdfpagelabels=TRUE, %renumber pdf pages correctly
    colorlinks,%no boxes
    citecolor=black,%make all links black
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\usepackage{ifthen} 
\renewcommand{\caption}[2][]{\singlespacing\ifthenelse{\equal{}{#1}}{\hangcaption{#2}}{\hangcaption[#1]{#2}}\normalspacing} 

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}

%\newcommand{\the}[0]{\superscript{th}}
\newcommand{\st}[0]{\superscript{st}}
\newcommand{\nd}[0]{\superscript{nd}}
\newcommand{\rd}[0]{\superscript{rd}}
\newcommand{\tm}[0]{\superscript{TM}}

%if you're having problems with overfull boxes, you may need to increase
%the tolerance to 9999
\tolerance=9999


%\bibliographystyle{IEEEbib}

%\renewcommand{\caption}[1]{\singlespacing\hangcaption{#1}\normalspacing}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\title {A Graph Theoretic Approach to Food Combination Problems}
\author {Michael Arden Nestrud}
\conferraldate {May}{2011}
\degreefield {Ph.D.}
\copyrightholder{Michael Arden Nestrud}
\copyrightyear{2011}

\begin{document}

\phantomsection
\maketitle
\phantomsection
\makecopyright
\phantomsection
\begin{abstract}

%\addcontentsline{toc}{subsection}{Abstract} %  adds "REFERENCES" to the table of content
Graph theory provides a useful representation of, and mathematical toolkit for, analyzing how things are connected together.  This collection of research investigates the use of graph theory as a representation of how foods are connected together.  The first two studies validate the subject questioning procedure used to create a graph model out of responses and the final study introduces a new approach to using this methodology to optimize field ration menus for the United States Army.

In the first study, we began by asking subjects whether or not pairs of ingredients would be appropriate to combine on a salad. Next, using graph theoretic methods, we predicted which combinations of 3-8 components should go together.  Subjects were then asked whether or not particular combinations were appropriate to combine on a salad. A paired Wilcoxon test between the predicted and non-predicted combinations was significant for all combination sizes.

The second study tested the principle of supercombinatorality, i.e. that food combinations (of more than two items) that are fully compatible on a pairwise basis are more compatible than combinations that are not fully compatible pairwise. This study extended the previous findings to group data. Purchase intent responses to pairs of different pizza toppings were collected and used to predict pizzas (with one to 6 toppings) that would appeal to the entire group. Results showed purchase interest to be higher for the predicted pizzas than for non predicted pizzas supporting the supercombinatorality principle. 

The final study extends the graph theory representation to military rations known as Meal-Ready-to-Eat or MREs™.  MRE™ menus are composed of 11 different food categories (entr\'{e}e, side, snack, etc.) and there are multiple items available in each category.  From these items there are over 22 billion potential menus.  Categories and items were screened to create a list of the most important ones and we asked soldiers whether or not pairwise combinations of components were appropriate to combine in a meal.  Using graph theoretic tools, predictions were made of optimal MRE™ menus and rankings were attached to prediction in order to assist the product developers in screening old and new menu concepts. 
\end{abstract}

\phantomsection
\begin{biosketch}
Michael Arden Nestrud grew up in Little Rock, Arkansas.  His passion for both science and cooking led him first to the Culinary Institute of America where he graduated with an Associate Degree in Occupational Studies in 2004.  He then was awarded a Teaching Fellowship at the CIA where he was the Sous Chef of the American Bounty Restaurant from 2004-2005, working under the mentorship of Chef William Phillips.  It was during this time he began formulating ideas regarding the perception of food from the culinary arts perspective, and his love for trigeminal irritants (e.g. spicy chiles) developed.  After the CIA, Michael went to Cornell University to study Food Science because he knew he wanted to build a scientific background of food processes.  During his time as an undergraduate he began working with Dr. Harry Lawless and found his calling studying human perception of the eating experience.  As an undergraduate, Michael and Harry published the first peer reviewed study comparing Chef and Consumer palates, and Michael also conducted research on perceptual mapping techniques and novel flavor compounds.  After he completed his Bachlor of Science (magna cum laude) in 2008 he was awarded a State University of New York Ph. D. Fellowship, which allowed him to continue his work with Dr. Lawless at Cornell.  

\end{biosketch}
\phantomsection
\begin{dedication}
This work is dedicated to my beautiful and loving wife, Effie.
\end{dedication}
\phantomsection
\begin{acknowledgements}

I would like to thank Dr. Harry Lawless, for being a teacher, mentor, friend and match-maker for all the years we’ve been working together.  I look forward to continuing our friendship.  I owe Dr. Bruce Halpern for his encouragement and advice throughout my time at Cornell.  Dr. Terry Acree's advice, wit and candidness has improved my research skills and my gratitude goes to Dr. Paul Velleman for sharing some of his incredible statistical knowledge with me during the course of my Ph. D. work.  

There are a few individuals whose assistance has been greatly appreciated.  I owe Dr. John Ennis of the Institute for Perception for his expertise and kind encouragement.  I appreciate the mentorship of Dr. Armand Cardello at the U.S. Army Research, Development and Engineering Laboratory and Dr. Daniel Ennis, also at the Institute for Perception.  At Cornell, thank you Kathy, Marva, Janette, Matt, Shelly, Denise and all of the professors and labmates whom have inspired and helped me over the years.  

My family always provides me support and encouragement.  Had it not been for them I would never habe been able to realize my dreams.  Thank you Terry, Rick, Elizabeth, Sara and Matthew.  

I owe a special thanks to my favorite labmate,  Effie (Epke) Nestrud.  Had she not chosen to go to Cornell for her graduate work my life would not be the same.  Her patience, support and smile means more to me than anyone will ever know.  I love you.

\end{acknowledgements}
\phantomsection
\contentspage
\phantomsection
\tablelistpage
\phantomsection
\figurelistpage

\normalspacing \setcounter{page}{1} \pagenumbering{arabic}
\pagestyle{cornell} \addtolength{\parskip}{0.5\baselineskip}

\include{tex/introduction}

\include{tex/study_objectives}

\include{tex/chapter_3}
\include{tex/chapter_4}
\include{tex/chapter_5}

\include{tex/discussion}


\end{document}
